### 2017-02-24 ResearchNotes/data.tex
Moved experiments to this repository
Adds statistics
Adds text on statistics
Adds er model of data to notes
Updated Research Notes

\TODO{Some information is missing for this sheet}

@@

\begin{itemize}
    \item \texttt{name\_c} - Name of the course
    \item \texttt{name\_s} - Name of the student
    \item \texttt{id\_c} - Id of the course
    \item \texttt{n\_resrc\_c} - Number of resources in the course
    \item \texttt{n\_actv\_c} - Number of activities in the course
    \item \texttt{id\_s} - Id of the student
    \item \texttt{n\_cons\_s} - \TODO{}
    \item \texttt{n\_subm\_s} - \TODO{}
    \item \texttt{result\_s} - Results of that student in that course
\end{itemize}

@@

\TODO{Fields in between}

@@

\begin{itemize}
    \item \texttt{course} - Course's id
    \item \texttt{Cod Moodle} - Course's Code in the Moodle
    \item \texttt{Cod Siiue} - Course's Code
    \item \texttt{min} - First activity of course
    \item \texttt{max} - Last activity of course
    \item \texttt{int} - Interval between first and last activity of course
    \item \texttt{actsub}
    \item \texttt{actcons}
    \item \texttt{nactsubd}
    \item \texttt{consal}
    \item \texttt{consdoc}
    \item \texttt{subal}
    \item \texttt{subdoc}
    \item \texttt{nalu}
    \item \texttt{ndoc}
    \item \texttt{InscSIIUE} - Number of students who enrolled
    \item \texttt{Aprov} - Number of students who got approved
    \item \texttt{Dep} - Department of the course
\end{itemize}

@@

% =============================================================================
\section{Objects, Entities, and Features}

@@

\subsection{Courses}

@@

\subsection{Moodle Users - Students, and Professors}

@@

\subsection{Results}

@@

\subsection{Moodle Logs}

@@

% CoursesGeneral.csv
% CoursesEntriesOverview.csv
% MoodleUsers.csv
% Students.csv
% CoursesStudents.csv
% Results.csv
% MoodleLogs.csv
% CoursesNoMoodle.csv

>>>>

@@

\begin{itemize}
    \item \texttt{name\_c} - Name of the course
    \item \texttt{name\_s} - Name of the student
    \item \texttt{id\_c} - Id of the course
    \item \texttt{n\_resrc\_c} - Number of resources (files, urls, etc)
    \item \texttt{n\_actv\_c} - Number of activities (forums, quizzes, etc)
    \item \texttt{id\_s} - Student's id
    \item \texttt{n\_cons\_s} - Number of views
    \item \texttt{n\_subm\_s} - Number of submissions
    \item \texttt{result\_s} - Results of that student in that course
\end{itemize}

@@

@@

\begin{itemize}
    \item \texttt{course} - Course's id
    \item \texttt{Cod Moodle} - Course's Code in the Moodle
    \item \texttt{Cod Siiue} - Course's Code
    \item \texttt{min} - First activity of course
    \item \texttt{max} - Last activity of course
    \item \texttt{int} - Interval between first and last activity of course
    \item \texttt{actsub} - Number of Submission Activities(Same value ad above)
    \item \texttt{actcons} - Number of views (Same as resources)
    \item \texttt{nactsubd} - Number of different activities
    \item \texttt{consal} - Student views
    \item \texttt{consdoc} - Professor views
    \item \texttt{subal} - Student submission
    \item \texttt{subdoc} - Professor submission
    \item \texttt{nalu} - Number of students in the course
    \item \texttt{ndoc} - Number of professors in the course
    \item \texttt{InscSIIUE} - Number of students who enrolled
    \item \texttt{Aprov} - Number of students who got approved
    \item \texttt{Dep} - Department of the course
\end{itemize}

@@

% =============================================================================
\section{Objects, Entities, and Features}
\label{sec:objs_ents_feat}

@@

\subsection{Courses}
\label{sec:data_courses}

@@

Courses have different values for credits. The statistic program
\texttt{stat\_001} lists number of courses with a given value for credits.
Table~\ref{tab:courses_credits} shows that count.

    \begin{tabular}{| l | r |}
        \hline
        Credits & Number of Courses \\ \hline
        1       & 3                 \\ \hline
        2       & 3                 \\ \hline
        3       & 3                 \\ \hline
        5       & 6                 \\ \hline
        6       & 46                \\ \hline
        7.5     & 12                \\ \hline
        12      & 2                 \\ \hline
        15      & 2                 \\ \hline
    \end{tabular}

    \caption
        [Number of courses group by credits]
        {Number of courses group by credits.}

    \label{tab:courses_credits}
\end{table}

\subsection{Moodle Users - Students, and Professors}
\label{ref:moodle_users}

@@

\subsection{Results}
\label{sec:results}

@@

\subsection{Moodle Logs}
\label{sec:logs}

@@

The data stored in CSV files from which any statistics are calculated and
experiments are executed. The data is also organized following a relational
paradigm, even if the data is not stored in a relational database.

The following sections describe which datasets store the data of the various
objects as described in section~\ref{sec:objs_ents_feat}. In the end of this
section, figure\ref{fig:er} shows the relational model of the various datasets.

\subsection{Courses Datasets}

Data on the courses is mostly store in the following dataset files:

\begin{itemize}
    \item \texttt{CoursesEntriesOverview}
    \item \texttt{CoursesGeneral}
    \item \texttt{CoursesNoMoodle}
    \item \texttt{CoursesStudents}
\end{itemize}

The first dataset contains mostly what is found in the original
\texttt{ResultadosUCMoodle} dataset. The second dataset contains general
information on each course, namely the three codes that identify each course,
the course name, regime, credits, etc.

The \texttt{CoursesNoMoodle} dataset simply contains a listing of courses that
have no moodle. These courses aren't very important since no other information
on them is available. But they are still kept in the processed datasets.

The \texttt{CoursesStudents} dataset contains one entry for each course. Each
entry states the total number of students of that course, the total number of
approved students, and the approval ration for that course. This information
would easily be calculated from other datasets in this repository, but it is
kept here since it was present in the original datasets.

\subsection{Moodle Users Datasets}

The following three datasets store information on the Moodle users:

\begin{itemize}
    \item \texttt{MoodleUsers}
    \item \texttt{Students}
\end{itemize}

Each Moodle user has a username, an actual name, and a role. That information
is stored in \texttt{MoodleUsers}. Students have the fields stated in
section~\ref{ref:moodle_users}, and those are stored in the \texttt{Students}
dataset.

\subsection{Results and Profiling Datasets}

Results are mostly stored in the \texttt{Results} dataset, but some other
information is stored in \texttt{Profile}.

The results consist of the fields stated in section~\ref{sec:results}.

\TODO{Talk about the profile dataset}

\subsection{Moodle Logs Dataset}

The logs dataset in \texttt{MoodleLogs} contain the entries as described in
section~\ref{sec:logs}.

\begin{figure}[h!]
    \centering

    \includegraphics[width=\linewidth]{../ER/er.pdf}

    \caption
        [Relational model for processed data repository]
        {Relational model for processed data repository.}

    \label{fig:er}
\end{figure}

### 2017-02-24 ResearchNotes/papers.tex
Updated Research Notes

This section contain long comments about the first papers which were explored
for this project.

>>>>

This section contain long comments about the first papers which were explored
for this project. Some of the comments are structures as a five paragraph essay
having the sections:

\begin{itemize}
    \item Introduction
    \item Exposure
    \item Arguments for
    \item Arguments against
    \item Conclusions
\end{itemize}

Other simply have one big comment.

As time went on, the necessity for analysing individual papers dropped, so the
number of papers that have individual comments in here is lesses than the total
number of papers in the project.

The papers listed in here are about Data Mining done to Moodle data. Each paper
is identified by the code \texttt{IND\_XXX}, where \texttt{XXX} is a number
with 3 leading zeros. Each paper is also identified by a reference in the
references section. As some papers reference each other, these references are
kept in the comments. The reason to identify a particular paper with a code is
because it makes it easy to store them in disk due to their long names.

Note that the number in \texttt{IND\_XXX} doesn't imply an order in the papers
listed in the document. Also, just because there is a paper in
\texttt{IND\_904} and a paper \texttt{IND\_906}, that doesn't imply that a
paper \texttt{IND\_905} needs to exists in the document.

### 2017-02-24 ResearchNotes/stat_exps.tex
Updated Research Notes

@@

>>>>

This section contains simple statistical analysis done to the data to better
understand it.

@@

This section contains Data Mining tasks done to the data. Each task doesn't
just use one of the datasets (\texttt{CSV} files), rather, it creates datasets
from existing ones and also calculates new fields.

\subsection{\texttt{EXP\_001} - \textit{Pending Name}}

\TODO{This experiment isn't finished yet.}

In this experiment datasets are build to represent a student's activity in a
given course and it's final outcome. The first dataset simply as a binary class
representing if the student was approved or not. The second has the following
classes:

\begin{itemize}
    \item $ [0, 10[ $
    \item $ [10, 12[ $
    \item $ [12, 14[ $
    \item $ [14, 16[ $
    \item $ [16, 18[ $
    \item $ [18, 20] $
\end{itemize}

The datasets used to build the experiment sets are \textit{Students},
\textit{CoursesGeneral}, \textit{MoodleLogs}, and \textit{Results}. The
tables~\ref{tab:exp_001} shows the fields of the built datasets, their types,
and origins. Note that the origin of some fields is \textit{Calculated}, this
is not a dataset, but rather is used to indicate that that field was especially
computed for this specific experiment.

    \begin{tabular}{| l | l | l |}
        \hline
        \textbf{Field}    & \textbf{Source Dataset}    & \textbf{Type} \\ \hline
        StudentsNumber    & Student                    & Number        \\ \hline
        EnrollementCount  & Student                    & Number        \\ \hline
        StudentType       & Student                    & Enumerated    \\ \hline
        CourseCodeSiiue   & CoursesGeneral             & String        \\ \hline
        Semester          & CoursesGeneral             & Enumerated    \\ \hline
        Season            & CoursesGeneral             & Enumerated    \\ \hline
        TotalActsOnCourse & Calculated From MoodleLogs & Number        \\ \hline
        CActsOnCourse     & Calculated From MoodleLogs & Number        \\ \hline
        RActsOnCourse     & Calculated From MoodleLogs & Number        \\ \hline
        UActsOnCourse     & Calculated From MoodleLogs & Number        \\ \hline
        DActsOnCourse     & Calculated From MoodleLogs & Number        \\ \hline
        Class             & Calculated From Results    & Binary        \\ \hline
    \end{tabular}

    \caption
        []
        {}

    \label{tab:exp_001}
\end{table}

% (A quick first review)
%
% The first dataset has a flaw. It groups students and courses together to predicts grades from those courses. That doesn't really make sense....
%
% Student's usage data about a single course should predict grades on that course alone.
%
% The same goes for clustering. Doesn't make sense to cluster this.
%
% Check the number of students per course. If a given course has a lot of students with approvals, run a classification for that course only.
%
% Also, resample.

\subsection{\texttt{EXP\_002} - \textit{Pending Name}}

\TODO{This experiment isn't finished yet.}

\subsection{\texttt{EXP\_003} - \textit{Pending Name}}

    \begin{tabular}{| l | l | l |}
        \hline
        \textbf{Field}    & \textbf{Source Dataset}    & \textbf{Type} \\ \hline
        StudentsNumber    & Student                    & Number        \\ \hline
        EnrolledCourses   & Calculated From Results    & Number        \\ \hline
        ApprovedCourses   & Calculated From Results    & Number        \\ \hline
        TotalActsOnCourse & Calculated From MoodleLogs & Number        \\ \hline
        CActsOnCourse     & Calculated From MoodleLogs & Number        \\ \hline
        RActsOnCourse     & Calculated From MoodleLogs & Number        \\ \hline
        UActsOnCourse     & Calculated From MoodleLogs & Number        \\ \hline
        DActsOnCourse     & Calculated From MoodleLogs & Number        \\ \hline
    \end{tabular}

    \caption
        []
        {}

    \label{tab:exp_003}
\end{table}

\TODO{This experiment isn't finished yet.}
